Figures

### 2020-03-04 figures/08_exploratory_dotplot.Rmd
use non abs correlation values

dt_tp_hmap_abs <- mutate_all(dt_tp_hmap, abs) %>%
  data.frame()
row.names(dt_tp_hmap_abs) <- rowcol_order
pheatmap::pheatmap(
  t(dt_tp_hmap_abs),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
```

>>>>

# dt_tp_hmap_abs <- mutate_all(dt_tp_hmap, abs) %>%
#   data.frame()
# row.names(dt_tp_hmap_abs) <- rowcol_order
# pheatmap::pheatmap(
#   t(dt_tp_hmap_abs),
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                             "Reds"))(100),
#   cluster_cols = TRUE, cluster_rows = TRUE,
#   na.col = "grey",
#   cellheight = 7)

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 8, cellwidth = 8, treeheight_col = 20, treeheight_row = 40)
```
